Modeling vertical-axis cross-flow turbine wakes

### 2015-07-22 paper.tex
Add goals, but kind of shaky
Add to goals, remove ALM, use SA abbrev., and discuss SA free stream

    \item Can ALM--RANS be used for array design?

@@

@@

The flow field was modeled using the Reynolds-averaged Navier--Stokes equations,
employing two different turbulence models--Menter's $k$--$\omega$ SST
\cite{Menter1994} and the Spalart--Allmaras one equation model
\cite{Spalart1992}. The SST model was chosen due to its prominence in the
literature for simulating separating flows, which we assumed to be present in
the current problem in the form of dynamic stall. The Spalart--Allmaras model
was shown by Ferreira et al. \cite{Ferreira2007} to match experimental particle
image velocimetry (PIV) results for a CFT in dynamic stall, though this was a
somewhat low Reynolds number case ($5 \times 10^4$).

@@

>>>>

@@

    \item Does 3-D RANS realize the proper wake recovery proportions? This would
    imply it could be a very accurate model if used in DES.

Goals:

    \item Evaluate modern computational fluid dynamics techniques for predicting
    the dynamic loading on cross-flow turbine blades.

    \item If possible, accurately predict the turbine from the perspective as a
    wake generator, such that the results can be used to develop low-order
    models.

@@

The flow field was modeled using the Reynolds-averaged Navier--Stokes equations,
employing two different turbulence models--Menter's $k$--$\omega$ SST
\cite{Menter1994} and the Spalart--Allmaras (SA) one equation model
\cite{Spalart1992}. The SST model was chosen due to its prominence in the
literature for simulating separating flows, which we assumed to be present in
the current problem in the form of dynamic stall. The SA model was shown by
Ferreira et al. \cite{Ferreira2007} to match experimental particle image
velocimetry (PIV) results for a CFT in dynamic stall, though this was a somewhat
low Reynolds number case ($5 \times 10^4$).

@@

For the SA model, the turbulence transport variable $\tilde{\nu}$, is ideally
zero in the free stream \cite{Spalart1992}, though others recommend using
$\tilde{\nu}/\nu \approx 3$--$5$ for fully turbulent simulations
\cite{Spalart2007}.
